SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all

### 2023-01-12 SI.tex
Update text and suthors

\title{SUPPLEMENTARY INFORMATION: NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration}

\author[1]{Anne Kiirikki}
\author[2]{...}
\author[1,*]{O. H. Samuli Ollila}
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}
\affil[1]{University of Helsinki, Institute of Biotechonology, Helsinki, Finland}
\affil[2]{Affiliation, department, city, postcode, country}

@@

\begin{figure}[!h]
    \centerfloat
    \includegraphics[width = 180mm]{Figures/QualityCorrelationsSI.pdf}
    \caption{Dependence of form factor, electron density profiles along membrane normal, and C-H bond orderparameters (from top to bottom) on simulation box size with different cholesterol concentration. }
    \label{fig:QualityCorrelationsSI}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width = 180mm]{Figures/permeationSI.pdf}
    \caption{a) Structure of an overlay databank. 
    More detailed structure of the layer 2 in the NMRlipids databank is illustrated in Fig.~\ref{DatabankStructure} in the SI.
    b) Distribution of the lengths of the trajectories, total number of trajectories and total lenght of the simulations in the NMRlipids databank.
    c) Distribution of lipids present in the trajectories in the NMRlipids databank. Lipids occuring in five or less simulations ('others') are listed in the right. 
    d) Currently available binary mixtures in the NMRlipids databank. 
    e) Distribution of force fields in the simulations in the NMRlipids databank.
    The figures and numbers are created on 9th of May 2022.}
    \label{fig:permeationSI}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width = 180mm]{Figures/LateralDiffusionSI.pdf}
    \caption{a) Structure of an overlay databank. 
    More detailed structure of the layer 2 in the NMRlipids databank is illustrated in Fig.~\ref{DatabankStructure} in the SI.
    b) Distribution of the lengths of the trajectories, total number of trajectories and total lenght of the simulations in the NMRlipids databank.
    c) Distribution of lipids present in the trajectories in the NMRlipids databank. Lipids occuring in five or less simulations ('others') are listed in the right. 
    d) Currently available binary mixtures in the NMRlipids databank. 
    e) Distribution of force fields in the simulations in the NMRlipids databank.
    The figures and numbers are created on 9th of May 2022.}
    \label{fig:diffusionSI}
\end{figure}

>>>>

\title{SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all}

\author[1]{Anne Kiirikki}         %ORCID: ?
\author[2]{Hanne Antila}          %ORCID: 0000-0002-2474-5053
\author[2]{Lara Bort}             %ORCID: ?
\author[3]{Pavel Buslaev}         %ORCID: ?
\author[4]{Fernando Favela}
\author[5]{Tiago Mendes Ferreira}
\author[6,7]{Patrick Fuchs}
\author[8,9]{Rebeca Garcia-Fandino}
\author[2]{Ivan Gushchin}
%\author[2]{Matti Javanainen}      %ORCID: 0000-0003-4858-364X
\author[2]{Batuhan Kav}           %ORCID: ?
\author[2]{Milla Kurki}
\author[2]{Alexander Kuzmin}
\author[10,11]{Jesper Madsen}
\author[2]{Markus S. Miettinen}   %ORCID: 0000-0002-3999-4722
%\author[2]{...}                   %ORCID: ?
\author[12]{Thomas Piggot}
\author[2]{Suman Samantray}
\author[2]{Fabi{\'a}n Suarez-Leston}
\author[1,*]{O. H. Samuli Ollila} %ORCID: 0000-0002- 8728-1006
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}

\affil[1]{University of Helsinki, Institute of Biotechnology, Helsinki, Finland}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{Nanoscience Center and Department of Chemistry, University of Jyv{\"a}skyl{\"a}, P.O. Box 35, Jyv{\"a}skyl{\"a}, 40014 , Finland}
\affil[4]{Departamento de Ciencias B\'{a}sicas, Tecnol\'{o}gico Nacional de M\'{e}xico - ITS Zacatecas Occidente, Sombrerete, Zacatecas, 99102, M\'{e}xico}
\affil[5]{NMR group - Institute for Physics, Martin Luther University Halle-Wittenberg,  Halle (Saale), 06120, Germany}
\affil[6]{Sorbonne Universit{\'e}, Ecole Normale Sup{\'e}rieure, PSL University, CNRS, Laboratoire des Biomol{\'e}cules (LBM), Paris, 75005, France}
\affil[7]{Universit{\'e} de Paris, UFR Sciences du Vivant, Paris, 75013, France}
\affil[8]{Center for Research in Biological Chemistry and Molecular Materials (CiQUS), Universidade de Santiago de Compostela,  Santiago de Compostela, E-15782, Spain}
\affil[9]{CIQUP, Centro de Investigação em Qu{\'i}mica, Departamento de Qu{\'i}mica e Bioqu{\'i}mica, Faculdade de Ci{\^e}ncias, Universidade do Porto, Porto, 4169-007, Portugal}
\affil[10]{Department of Chemistry, The University of Chicago, Chicago, Illinois, 60637, United States of America}
\affil[11]{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, 33612, United States of America}
\affil[12]{Chemistry, University of Southampton, Highfield, Southampton, SO17 1BJ, United Kingdom}

@@

\begin{figure}[!h]
    \centerfloat
    \includegraphics[width = 180mm]{Figures/QualityCorrelationsSI.pdf}
    \caption{Scatter plots and Pearson correlation coefficients, $r$, for the membrane area per lipid with X-ray scattering form factor minima (A and B), and for thickness with the average order parameter of the {\textit sn}-1 acyl chain (B) and with the second minimum from X-ray scattering form factors (D) extracted from the NMRlipids databank. All correlation coefficients have p-value below 0.001 as indicated by $^{***}$.}
    \label{fig:QualityCorrelationsSI}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width = 180mm]{Figures/permeationSI.pdf}
    \caption{Water permeation through membranes analyzed from the databank as a function of (A) hydration level, (B) fraction of cholesterol, (C) fraction of charged lipids, and (D) fraction of POPE in membrane. Values from simulations with non-zero permeation values are shown with blue dots. Histogrammed values are shown with black dots.
    }
    \label{fig:permeationSI}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width = 180mm]{Figures/LateralDiffusionSI.pdf}
    \caption{Lateral diffusion of water as a function of (A) area per lipid, (B) temperature, (C) membrane thickness, and (D) fraction of charged lipids in a membrane.}
    \label{fig:diffusionSI}
\end{figure}
